TBD

### 2021-02-19 outputs/paper/paper.Rmd
Update graph themes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)

@@

```{r Q1, echo = FALSE, message = FALSE}
#### Pie Chart ####
### Import cleaned business licences dataset
dfCleanBiz <- readr::read_csv("../../inputs/data/clean_business_licences.csv")
### Create data frame
dfBoroughs <- data.frame(
  group = dfCleanBiz$fsa,
  value = dfCleanBiz$n
)
### Calculate percentages
dfBoroughs <- dfBoroughs %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(dfBoroughs$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  arrange(desc(prop))
# print(dfBoroughs)
### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() + 
  geom_text(aes(y = ypos, label = percent(prop)), color = "white", size=3) +
  scale_fill_brewer(palette = "Paired")
```

```{r Q2, echo = FALSE, message = FALSE}
### "What best describes the scale of your restaurant?
### Small (full seating capacity is under 30)
### Medium (full seating capacity between 30 and 60)
### Large (full seating capacity is 60+) "

ggplot(data = all_simulated_dataset, mapping = aes (x = Q2)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Small", "Medium", "Large")) +
  labs(x = "Scale of Restaurant",
       y = "# of Restaurants",
       title = "Q2") +
  theme_minimal()
```

```{r Q3, echo = FALSE, message = FALSE}
### What best describes your restaurant segmentation?
### Fast-food/quick service
### Casual Dining
### Fine Dining
### Other

ggplot(data = all_simulated_dataset, mapping = aes (x = Q3)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Fine Dining", "Casual Dining", "Fast-food/quick service", "Other")) +
  labs(x = "Type of Restaurant",
       y = "# of Restaurants",
       title = "Q3") +
  theme_minimal()
```

```{r Q4, echo = FALSE, message = FALSE}
### How many years has your restaurant been in operation?
### 1-4 years
### 5-7 years
### 8-10 years
### 10 or more years

ggplot(data = all_simulated_dataset, mapping = aes (x = Q4)) +
  geom_bar() + coord_flip() +
  scale_x_discrete(limit = c ("1-4 years", "5-7 years", "8-10 years", "10 or more years")) +
  labs(x = "Years of Operation",
       y = "# of Restaurants",
       title = "Q4") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did revenue increase, decrease, or remain the same compared to last month?",
       y = "# of restaurants",
       title = "Q7",
       fill = "Type") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = "Q8",
       fill = "Type") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar(position = position_dodge(1)) +  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = "Q10",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "Other", "In-house delivery service", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Q11",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Was there a reduction in restaurant hours?",
       y = "# of restaurants",
       title = "Q12",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q13, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Hours Reduced per Week",
       y = "# of Restaurants",
       title = "Q13",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did you reduce the # of days you were open to the public between (start date) and (end date)?",
       y = "Y",
       title = "Q14",
       fill = "Legend") +
  theme_minimal()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "How many days per week did you reduce by?",
       y = "# of restaurants",
       title = "Q15",
       fill = "Legend") +
  theme_minimal()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(wesanderson)
library(RColorBrewer)
library(ggthemes)
library(scales)

@@

```{r regions, echo = FALSE, message = FALSE}
#### Pie Chart ####
### Import cleaned business licences dataset
dfCleanBiz <- readr::read_csv("../../inputs/data/clean_business_licences.csv")
### Create data frame
dfBoroughs <- data.frame(
  group = dfCleanBiz$fsa,
  value = dfCleanBiz$n
)
### Calculate percentages
dfBoroughs <- dfBoroughs %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(dfBoroughs$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  arrange(desc(prop))
dfBoroughs <- dfBoroughs[-c(10),]
# print(dfBoroughs)

### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y", start = 0) +
  theme_void() +
  geom_text(aes(x=1.65, y = ypos, label = percent(prop)), color = "black", size=2.8) +
  scale_fill_brewer(palette = "Set3") + 
  labs(fill = "Region", title = "Proportion of Restaurants in Toronto by Borough") +
  theme(plot.title = element_text(face = "bold"))
```

```{r Q1, echo = FALSE, message=FALSE}
ggplot(data = all_simulated_dataset, mapping = aes (x = Q1, fill = type)) +
  geom_bar() + coord_flip() +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  labs(fill = "Condition", title = "Q1")
```

```{r Q2, echo = FALSE, message = FALSE}
### "What best describes the scale of your restaurant?
### Small (full seating capacity is under 30)
### Medium (full seating capacity between 30 and 60)
### Large (full seating capacity is 60+) "
ggplot(data = all_simulated_dataset, mapping = aes (x = Q2, fill = type)) +
    geom_bar() +
  scale_x_discrete(limit = c ("Small", "Medium", "Large")) +
  labs(x = "Scale of Restaurant",
       y = "# of Restaurants",
       title = "Q2") +
  labs(fill = "Condition", title = "Q2") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

```{r Q3, echo = FALSE, message = FALSE}
### What best describes your restaurant segmentation?
### Fast-food/quick service
### Casual Dining
### Fine Dining
### Other
ggplot(data = all_simulated_dataset, mapping = aes (x = Q3, fill = type)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Fine Dining", "Casual Dining", "Fast-food/quick service", "Other")) +
  labs(x = "Type of Restaurant",
       y = "# of Restaurants",
       title = "Q3") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

```{r Q4, echo = FALSE, message = FALSE}
### How many years has your restaurant been in operation?
### 1-4 years
### 5-7 years
### 8-10 years
### 10 or more years
ggplot(data = all_simulated_dataset, mapping = aes (x = Q4, fill = type)) +
  geom_bar() + coord_flip() +
  scale_x_discrete(limit = c ("1-4 years", "5-7 years", "8-10 years", "10 or more years")) +
  labs(x = "Years of Operation",
       y = "# of Restaurants",
       title = "Q4") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Did revenue increase, decrease, or remain the same compared to last month?",
       y = "# of restaurants",
       title = "Q7",
       fill = "Type") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = "Q8",
       fill = "Type") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = "Q10",
       fill = "Legend") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "Other", "In-house delivery service", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Q11",
       fill = "Legend") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme_fivethirtyeight()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Was there a reduction in restaurant hours?",
       y = "# of restaurants",
       title = "Q12",
       fill = "Legend") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q13, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Hours Reduced per Week",
       y = "# of Restaurants",
       title = "Q13",
       fill = "Legend") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did you reduce the # of days you were open to the public between (start date) and (end date)?",
       y = "Y",
       title = "Q14",
       fill = "Legend") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "How many days per week did you reduce by?",
       y = "# of restaurants",
       title = "Q15",
       fill = "Legend") +
    scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight() 
```
